Hierarchical ARIMA

### 2020-08-18 KB_modeling.Rmd
Added comments changes from AR term

## Added new dataset for playoff
# broken up into 6 different factors
# - Won WS (1 team)
# - Lost WS (1 team)
# - Lost Semi (2 teams)
# - Lost Quarter (4 teams)
# - Lost WC (2 teams)    NOTE: wildcard game started in 2012 so this variable is only from 2012-2019.
# - No Playoffs (22 teams from 2004-2011 and 20 teams from 2012-2019)

@@

# NOTE to self: check this again to see if i did it right

annual_means <- lm(ghits_e1 ~ odds + winpct + attendance + payroll + lag(ghits_e1, 1), data = by_year) ## this should be an AR model, annual

# i used the lag function , but examples I see have used dynlm package

summary(annual_means)

@@

@@

@@

```{r}
final_model <- 
  dat  %>%
  lm(ghits_e2 ~ phase + is_playoffs:playoffs + lag(ghits_e2, 1), data = .) ## needs to be AR model instead, monthly

@@

@@

```{r}
dat %>%
  filter(team %in% CA_teams) %>%
  ggplot(aes(x = date, y = ghits_e3, color = team)) +
  geom_line()
```
```{r}
dat %>%
  filter(team %in% example_teams) %>%
  ggplot(aes(x = ghits_e3)) +
  geom_histogram() +
  facet_wrap(~team)
```

@@

>>>>

## Added new dataset for playoff: MLB_Postseason_Success.csv
# broken up into 6 different factors
# - Won WS (1 team)
# - Lost WS (1 team)
# - Lost Semi (2 teams)
# - Lost Quarter (4 teams)
# - Lost WC (2 teams)    NOTE: wildcard game started in 2012 so this variable is only from 2012-2019.
# - No Playoffs (22 teams from 2004-2011 and 20 teams from 2012-2019)

@@

# NOTE to self: check this again to see if i did it right
# i used the lag function , but examples I see have used dynlm package

annual_means <- lm(ghits_e1 ~ odds + winpct + attendance + payroll + lag(ghits_e1, 1), data = by_year) ## this should be an AR model
# annual_means <- lm(ghits_e1 ~ odds + winpct + attendance + payroll, data = by_year)

summary(annual_means)
```

@@

UPDATE: What changed after adding the AR term lagging one year?
Looks like odds,  winpct, and the lag are all good predictors of annual ghits now.  Payroll is no longer significant.

@@

UPDATE: What changed after adding AR term?
Looks like heavier spikes on the under predictions? Note sure why the spikes are so sharp. Is that okay?  Looks more sporadic because the lag accounts for the yearly cycle.

@@

```{r}
final_model <- 
  dat  %>%
  lm(ghits_e2 ~ phase + is_playoffs:playoffs + lag(ghits_e2, 1), data = .) ## needs to be AR model instead, monthly
  # lm(ghits_e2 ~ phase + is_playoffs:playoffs, data = .)

@@

UDPATE: Why is lost WS NA?  All variables are significant predictors of monthly ghits except winning WS.

@@

UPDATE: What changed when I added the lag on the previous month?
It seems like adding the lag term doesn't change this plot? Might be doing something wrong.

```{r}
dat %>%
  filter(team %in% CA_teams) %>%
  ggplot(aes(x = date, y = ghits_e3, color = team)) +
  geom_line()
```

```{r}
dat %>%
  filter(team %in% example_teams) %>%
  ggplot(aes(x = ghits_e3)) +
  geom_histogram() +
  facet_wrap(~team)
```

@@

UPDATE: AR did seem to help this underpredicting problem! The California team plot is much more sporadic.  The histograms are centered closer to 0.  And all the predictions seem to be closer than before!
